Kit Theory

### 2023-07-04 paper/paper.tex
Update.

  In both cases \texttt{\_∋\_} and \texttt{\_⊢\_} are instanciated to type
  \texttt{List (Sort Var) → Sort Var → Set}, so we can create a structure
  to axiomatize the common theory behind both of them.
  \LibCode\KKit

>>>>

  In both cases \texttt{\_∋\_} and \texttt{\_⊢\_} are instanciated to the type
  \LibCode\KScoped
  which allows us to create a structure to axiomatize the common
  theory behind both of them:
  \LibCode\KKit
